Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2021-11-22 doc/JFLA2022/paper.tex
reformulation in comparison section

The flip side of our approach is that we separate the Coq sources from the LaTeX sources that describe the code, and our use of snippet delimiters in the Coq source files may also lower source readability. For books and libraries with small scope and specialized audiences, distributing knowledge representations between sources and documentation formats the way we do in \Hydras may introduce overhead without providing complementary benefits.
%
More specifically, we currently distribute the book as a PDF generated by LaTeX with links to corresponding HTML documentation of the Coq sources generated by \coqdoc. This means that in contrast to Software Foundations, we cannot easily obtain a uniform single-format representation of all documentation.

>>>>

The flip side of our approach is that we separate the Coq sources from the LaTeX sources that describe the code, and our use of snippet delimiters in the Coq source files may lower source readability. For books and libraries with small scope and specialized audiences, distributing knowledge representations between sources and documentation formats the way we do in \Hydras may introduce overhead without providing complementary benefits.
%
More specifically, we currently distribute the book as a PDF generated by LaTeX that links to corresponding HTML documentation of the Coq sources generated by \coqdoc. In contrast, executable books such as Software Foundations can provide a single uniform HTML representation of both book contents and code.
